A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-10-13 05_calibration_data.Rmd
resample data

# filter for boating segment
data_recurse <- atl_filter_covariates(data = data_recurse,
  filters = c("between(UTCtime, '2020-08-24 11:13:00', '2020-08-24 12:36:11')"))

@@

# get recurse data for a 10m radius
recurse_stats <- getRecursions(data_recurse,
                               radius = 500, timeunits = "mins")

# assign to recurse data
data_recurse[, res_time := recurse_stats$residenceTime]
```

>>>>

# filter for boating segment
# data_recurse <- atl_filter_covariates(data = data_recurse,
#  filters = c("between(UTCtime, '2020-08-24 11:13:00', '2020-08-24 12:36:11')"))

# thin the data
data_recurse <- atl_thin_data(data = data_recurse,
                              interval = 30, id_columns = "TAG",
                              method = "resample")

@@

# get recurse data for a 10m radius
recurse_stats <- getRecursions(data_recurse,
                               radius = 100, timeunits = "mins")

# assign to recurse data
data_recurse[, res_time := recurse_stats$residenceTime]

# save recurse data
fwrite(data_recurse, file = "data/data_calib_recurse.csv")
```
